### 2023-09-08 3.Design/memcell.tex
onchip area begin + timediagram for memcell

@@

This circuit is pretty straight forward, when the input enable pin is high (up to $V_{dd}$), then the first switch is open and the capacitor is being charged, if it is low, then the switch is closed and the capacitor keeps the voltage and thus the analog data. When the output enable is high, the buffer (TODO : Explain in annexe ?) forwards the voltage stored in the capactor to the output pin without emptying the capacitor.

TODO : figure that explains the fonctionnement

>>>>

For this circuit the approximate onChip area :

\begin{equation}
  A_{memcell}=8\cdot A_{CMOS}+2\cdot A_{inv}+A_{opAmp}+A_{cap}
\end{equation}

With $A_{CMOS} = w\cdot l = 9\cdot 10^{-7} \cdot 6 \cdot 10^{-8} = 5.4 \cdot 10^{-14} m^2$ TODO check value w et l

@@

This circuit is pretty straight forward, when the input enable pin is high (up to $V_{dd}$), then the first switch is open and the capacitor is being charged, if it is low, then the switch is closed and the capacitor keeps the voltage and thus the analog data. When the output enable is high, the buffer (appendix \ref{apsec:buffer}) forwards the voltage stored in the capactor to the output pin without emptying the capacitor.

\begin{figure}[H]
  \centering
  \begin{tikztimingtable}
    Input data & x6D{$x_1$}6D{$x_2$}6D{$x_3$}x \\
    Input enable & xL2H2L3H7L2HLx\\
    Output enable & x3L2H4L5H1L3Hx\\
    Memory & xU4D{$x_1$}10D{$x_2$}3D{$x_3$}x \\
    Output data & x3U2D{$x_1$}4U5D{$x_2$}U3D{$x_3$}x \\
    \extracode
    \tablerules
    %\draw (0,0) circle (2pt); % Origin
    \begin{pgfonlayer}{background}
      \vertlines[help lines]{0.6,18.6}
      %\vertlines[red]{1.6,5.6,15.6}
      %\vertlines[blue]{3.6,9.6,15.6}
    \end{pgfonlayer}
  \end{tikztimingtable}
  \caption{Time diagram that shows the logic of the memory cell}
  \label{tim:memcell}
\end{figure}
